Leveraging Semantics for a Deep Web Question Answering System

### 2010-03-02 paper/semsearch10/paper.tex
Update of the introduction

\title{Leveraging Semantics for a Deep Web Question and Answering System} 
\numberofauthors{1}
\author{
	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
\email{\{ cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs \} @cise.ufl.edu}
}
\date{April 26,2010}

@@

\section{Introduction}
% Christan
- IEEE potentials article talks discussed the idea of using the beaten trail. \cite{5379671} To solve problems
- Typical search engines have several repeat queries.
- We believe that treating these repeat visits as special visits will enhance user search experience
- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering

>>>>

\title{Leveraging Semantics for a Deep Web Question Answering System} 
\numberofauthors{1}
\author{
	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
\email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}
}
\date{April 26,2010}

@@

\section{Introduction}
% Christan
- When traveling though a jungle to a destination, it is easy to get lost.  If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.  However if you are the \emph{n}th person, there is a beaten trail of the most commonly used path.
- IEEE potentials article talks discussed the idea of using the beaten trail. \cite{5379671} To solve problems
- Typical search engines have several repeat queries.
- We believe that treating these repeat visits as special visits will enhance user search experience
- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
-
